---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mortgager

<!-- badges: start -->
<!-- badges: end -->

This package obtains various values such as monthly mortgage payment amounts, downpayment amounts, minimum income required for affordable home-ownership etc.

## Installation

You can install the released version of mortgager with:

``` r
devtools::install_github("aseemdeodhar/mortgager")
```

## mortgager

Load the \code{mortgager} package with this line:

```{r example}
library(mortgager)
```

## Examples for each function:

### mortgager::monthlypayment()

\code{monthlypayment} calculates monthly home-ownership costs based on tax rates, interest rates, downpayment rate, and home cost price.

```{r}
monthlypayment(mortgage_rate = 3,
               property_tax = 12,
               home_price = 450000)
```

### mortgager::max_homeprice()

\code{max_homeprice} calculates maximum affordable home price based on annual income with a set monthly housing cost percentage (default is 30%).

```{r}
max_homeprice(annualinc = c(61000, 75000, 22330, 120000),
              mortgage_rate = 2.7,
              property_tax = 6)
```

### mortgager::downpayment()

\code{downpayment} calculates the total downpayment amount based on sale price and downpayment rate

```{r}
downpayment(home_price = 250000,
            downpayment_rate = 0.10)
```

### mortgager::min_anninc()

\code{min_anninc} calculates the minimum annual income required for total housing costs to remain at or below 30% of household income.

```{r}
min_anninc(2000)
```

### mortgager::burd_anninc()

\code{burd_anninc} calculates the minimum annual income required for total housing costs to remain at or below 50% of household income.

```{r}
burd_anninc(2000)
```
